```{r}
library(httr2)
library(dplyr)
```

```{r}
?httr2
```

code == "client"

1. Creat a request object with any paraphanalia

## Create a request

Get the url from the docs!

```{r}
req_users <- request('https://dummyjson.com/')
```

`body` can add content to send to the api
but that would be `POST` request
We are going to make a `GET` request
Our client is request to "get" stuff.

## Append user


```{r}
req_users <- request('https://dummyjson.com/') |> 
  req_url_path_append('users')

```


## Add header

Like "meta-data" for request
Adds extra instructions for the server

Here we say what type of data we want

```{r}
req_users <- request('https://dummyjson.com/') |> 
  req_url_path_append('users') |> 
  req_headers(Accept = 'application/json')

```


## A dry run?

User agent == "what type of clien"

Curl == underlying function used by httr2

```{r}
req_users |> 
  req_dry_run()
```

## Lets perform

```{r}
req_users <- request('https://dummyjson.com/') |> 
  req_url_path_append('users') |> 
  req_headers(Accept = 'application/json')

resp_users <- req_perform(req_users)
resp_users
```
200 OK - server says "Yes"
404    -> sever syas "No" - page not found - probably our fault
500    -> the server has a problem - not our fault


## Get our data out

```{r}
users_list <- resp_body_json(resp_users)
users_list
names(users_list)

users_list[['users']]
users_list$users[3]
users_list$users[[3]]

```

```{r}
users_df <- resp_body_json(resp_users,
                           simplifyVector = TRUE)
users_df

```

## Lets use usual TV suspects

```{r}
users_df <- users_df$users

users_by_blood_group <- users_df |> 
  group_by(bloodGroup) |> 
  summarize(count = n()) |> 
  arrange(desc(count))

users_by_blood_group
```

## JSON data

Javacript Object Notation

Lightweight, plaintext, JS 


Server sent us JSON data
`rep_body_json()` takes that and converts into R flavour

JS uses camel case by convention

